---
title: "Sino Yoga Predictive Analysis"
subtitle: "Qualtrics IRB Survey"
author: "Jae Jung"
date: last-modified
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: false
    theme: cosmo
    embed-resources: true
execute:
  warning: false
  message: false
---

# Client Overview

Sino Yoga is a cross-cultural yoga and wellness brand founded by Yang Qi, integrating Traditional Chinese Medicine with yoga practice through her signature Five-Element Meridian Yoga method. The brand is expanding from China into the U.S. market and uses YouTube (@Sinoyoga) as its primary discovery channel, with the long-term goal of monetizing its audience through tiered, subscription-based yoga memberships. Sino Yoga maintains a multi-platform digital presence across YouTube, WeChat, a newly launched Facebook page, and the [Sino Yoga website](https://sinoyoga.org/en-us).

## Business Objectives

Sino Yoga's primary growth objectives shape the analytical scope of this engagement:

-   Increase brand awareness across markets
-   Build a cohesive multi-channel platform experience
-   Grow subscriber base across YouTube and the website
-   Strengthen brand visibility in U.S. and international markets
-   Improve viewer retention and returning audience rate
-   Develop a sustainable monetization pathway

# Business Problem

> Sino Yoga has a lack of a structured, data driven digital growth strategy that limits visibility, engagement, and revenue. The brand needs to enhance brand visibility, increase audience engagement, and develop sustainable membership monetization, while addressing multi-channel integration challenges that support long-term growth.

## Membership Monetization

# Data Wrangling

## Data Importing

### Load Libraries

```{r}
#| message: false
#| warning: false
library(haven)
library(tidyverse)
library(dplyr)
library(janitor)
library(lubridate)
```

## Read CSV

```{r}
msdm_data <- read.csv("msdm_cleandata.csv")
head(msdm_data,3)
#view(msdm_data)
#str(msdm_data)
```

## Clean Data Part 1

```{r}
#Clean Variable Names
SurveyData <- clean_names(msdm_data) |>  #clean SurveyData names
              clean_names(case= "upper_camel") #clean up using upper_camel

#head(SurveyData) #check to see changes made to SurveyData

#change startdate to Date
SurveyData$RecordedDate <- as.Date(SurveyData$RecordedDate,
  format = "%m/%d/%Y %H:%M:%S")

str(SurveyData$RecordedDate)
#head(SurveyData)
```

## Clean Survey Variables

```{r}
#| message: false
#| warning: false
#change variable names
CleanSurveyData <- SurveyData |>
  rename(
    PracticeYogaInterest = Question1,
    YogaExperience = Question2,
    YogaActivityGroup= Question3_1,
    YogaActivityPrivate= Question3_2,
    YogaActivityOnline= Question3_3,
    YogaActivityPreRec= Question3_4,
    YogaActivityBook= Question3_5,
    YogaActivityFriend= Question3_6,
    YogaActivitySelfTaught= Question3_7,
    YogaActivityOther= Question3_8,
    YogaActivitiesOtherText = Question3_8Text,
    YogaFrequency = Question4,
    YogaContent = Question5_1,
    YogaLifestyle = Question5_2,
    YogaInfoSeeking = Question5_3,
    PrefVideoShorts = Question6_1,
    PrefVideoShortVideo = Question6_2,
    PrefVideoMedium = Question6_3,
    PrefVideoFulllength = Question6_4,
    BegFlowInterest = Question7_1,
    StressReliefInterest = Question7_2,
    TradChineseInterest = Question7_3,
    BreathworkInterest = Question7_4,
    FullLengthInterest = Question7_5,
    MonthProgramInterest = Question7_6,
    ShortDailyInterest = Question7_7,
    MemberInterest = Question8,
    WillingnessToPay = Question9,
    WillingnessToPayText = Question9_5Text,
    VisitLikelihood = Question10,
    YoutubeSocial = Question11_1,
    InstagramSocial = Question11_2,
    TIkTokSocial = Question11_3,
    FacebookSocial= Question11_4,
    PinterestSocial = Question11_5,
    AgeGroup = Question12,
    Gender = Question13,
    IncomeBracket = Question14,
    EnglishLang = Question15_1,
    MandarinLang = Question15_2,
    CantoneseLang = Question15_3,
    SpanishLang= Question15_4,
    OtherLang = Question15_5,
    OtherLangeText = Question15_5Text,
    Country = Question16,
    SearchInterest = Question17
  )

head(CleanSurveyData,3)
```

## Clean Data Part 2

```{r}
#| message: false
#| warning: false
#Clean Data
#recode any values not recoded on SPSS and Qualtrics
CleanSurveyData$MemberInterest <-
  recode(
    CleanSurveyData$MemberInterest,
    `27` = 1,
    `28` = 2,
    `29` = 3
  )

#Clean country to categorical
CleanSurveyData$Country <-
  factor(
    CleanSurveyData$Country,
    levels = c(31,185,187),
    labels = c("China","Taiwan","United States")
  )

#clean gender 
CleanSurveyData$Gender <- as.factor(CleanSurveyData$Gender)


#join text and regular wtp
CleanSurveyDataJoin<- CleanSurveyData |>
  mutate(
    WillingnessToPayText= as.numeric(WillingnessToPayText),
    WtpDollars= coalesce(WtpDollars, WillingnessToPayText)
  )

head(CleanSurveyDataJoin$WtpDollars,10)
```

## Full Messy Correlation Matrix

```{r}
#| message: false
#| warning: false
library(corrplot)
#PairWise Correlation of Continuous Variables
#new Data Set to keep everything numeric
str(CleanSurveyData)
DataForCorAnalysisAll = CleanSurveyDataJoin |>
                       select(where(is.numeric))
CorMatrixAll = cor(DataForCorAnalysisAll, use= "pairwise.complete.obs")

corrplot(CorMatrixAll, method = 'shade', addCoef.col = 'black', type = 'full', number.cex = 0.6, order = 'original', diag= FALSE)
```

## Correlation Matrix Cleaned

```{r}
#Narrow Down Correlation Matrix
DataForCorAnalysis = CleanSurveyDataJoin |>
                     select(YogaExperience, WillingnessToPay,SearchInterest,YogaContent,MandarinLang, VisitLikelihood, WtpDollars,MemberInterest, YogaFrequency, PrefVideoShorts)

CorMatrix = cor(DataForCorAnalysis, use= "pairwise.complete.obs")
corrplot(CorMatrix, method = 'shade', addCoef.col = 'black', type = 'full', number.cex = 0.6, order = 'original', diag= FALSE)
```

```{r}
#membership interest of people who answered all 4 survey questions
#model_data <- CleanSurveyData|> #new data to use for predicitive analysis
#  select(MembershipInterest,AgeGroup,Gender, YogaExperience) |> #filtering 4 survey #questions
#str(model_data) #shows 50 obs of 4 variables
```

## Linear Regressions

```{r}
#Linear Regression 1
#| message: false
#| warning: false
#Linear Regresssion
set.seed(123)
#library(tidymodels)
library(rio)

ModelSurvey= lm(WtpDollars ~ YogaFrequency, CleanSurveyDataJoin)

summary(ModelSurvey)
#R-squared 0.10
#Adjusted r-squared 0.08
#Overall model is significant (p= 0.030 < 0.05)
#YogaFrequency = 0.882 (p = 0.030)
#If everything else stays the same, a 1 point increase in yoga frequency increases willingness to pay by about $0.88 
#People who practice yoga more frequently are willing to pay more 
#Focus on encouraging consistent yoga practice through series, challenges and weekly classes

```

```{r}
#Linear Regresssion 2
#| message: false
#| warning: false
set.seed(123)
ModelSurvey2= lm(WtpDollars ~ VisitLikelihood, CleanSurveyDataJoin)

summary(ModelSurvey2)
#R-squared = 0.145
#Adjusted R-squared = 0.126
#Overall model is significant (p = 0.008 < 0.05)
#VisitLikelihood = 1.187 (p = 0.008)
#If everything else stays the same, a 1 point increase in visit likelihood increases willingness to pay by about $1.19
#People who are more likely to visit Sino Yoga are willing to pay more
#Focus on driving website visits through YouTube CTAs, email, and community engagement
```

```{r}
#Linear Regresssion 3
#| message: false
#| warning: false
set.seed(123)
ModelSurvey3= lm(WtpDollars ~ VisitLikelihood+YogaFrequency, CleanSurveyDataJoin)

summary(ModelSurvey3)
#R-squared = 0.189
#Adjusted R-squared = 0.152
#Overall model is significant (p = 0.010 < 0.05)
#VisitLikelihood remains significant
#YogaFrequency is no longer significant after controlling for visit likelihood
#People who are more engaged with Sino Yoga are willing to pay more than those who simply practice yoga frequently
#Focus on increasing engagement with the Sino Yoga brand and moving viewers toward memberships
```

```{r}
#Linear Regresssion 4
#| message: false
#| warning: false
set.seed(123)
ModelSurvey4= lm(WtpDollars ~ AgeGroup+Gender+YogaFrequency+MandarinLang, CleanSurveyDataJoin)

summary(ModelSurvey4)
#R-squared = 0.236
#Adjusted R-squared = 0.161
#Overall model is significant (p = 0.024 < 0.05)
#AgeGroup = -1.853 (p = 0.018)
#YogaFrequency = 1.054 (p = 0.012)
#MandarinLang is marginally significant (p = 0.085)
#Younger respondents and more frequent yoga practitioners are willing to pay more
#Continue bilingual content and encourage regular yoga practice
```

```{r}
#Linear Regresssion 5
#| message: false
#| warning: false
set.seed(123)
ModelSurvey5= lm(WtpDollars ~ AgeGroup+Gender+YogaFrequency+MandarinLang+Country, CleanSurveyDataJoin)

summary(ModelSurvey5)
#R-squared = 0.329
#Adjusted R-squared = 0.203
#Overall model is significant (p = 0.035 < 0.05)
#MandarinLang = 2.086 (p = 0.010)
#Country is not significant
#Mandarin-speaking respondents are willing to pay about $2.09 more than non-Mandarin speakers
#Language matters more than country
#Continue investing in bilingual English and Traditional Chinese content
```

```{r}
#Linear Regresssion 6
#| message: false
#| warning: false
set.seed(123)
ModelSurvey6= lm(WtpDollars ~ AgeGroup+Gender+YogaFrequency+MandarinLang+PracticeYogaInterest, CleanSurveyDataJoin)

summary(ModelSurvey6)
#R-squared = 0.246
#Adjusted R-squared = 0.151
#Overall model is significant (p = 0.039 < 0.05)
#AgeGroup = -1.847 (p = 0.019)
#YogaFrequency = 1.152 (p = 0.010)
#PracticeYogaInterest is not significant (p = 0.468)
#Simply being interested in yoga does not increase willingness to pay
#People who actually practice yoga more frequently are willing to pay more
#Focus on building consistent practice habits instead of only generating interest
```

```{r}
#Linear Regresssion 7
#| message: false
#| warning: false
set.seed(123)
ModelSurvey7= lm(WtpDollars ~ AgeGroup+Gender+YogaFrequency+MandarinLang+PracticeYogaInterest+YoutubeSocial, CleanSurveyDataJoin)

summary(ModelSurvey7)
#R-squared = 0.257
#Adjusted R-squared = 0.133
#Overall model is NOT significant (p = 0.081 > 0.05)
#YoutubeSocial is not significant (p = 0.544)
#AgeGroup and YogaFrequency remain significant
#Finding Sino Yoga through YouTube/social media alone does not increase willingness to pay
#Focus on retaining viewers and converting them into active community members rather than only acquiring new viewers
```

## Random Forest (Failed)

```{r}
#Random Forest Predictor Failed because of Sample Size
#remove NA respondents
set.seed(123)
library(randomForest)

model_data <- CleanSurveyDataJoin|> #new data to use for predicitive analysis
                 select(WtpDollars,YogaFrequency,AgeGroup,Gender, VisitLikelihood, YogaExperience,PracticeYogaInterest, MemberInterest) |> #select 
                 na.omit()


rf <- randomForest(
  WtpDollars ~ .,
  data = model_data,
  importance = TRUE
)

varImpPlot(rf)
print(rf)
```

## Decision Tree

```{r}
#| message: false
#| warning: false
library(rpart)
library(rpart.plot)
set.seed(123)

model_data2 <- CleanSurveyDataJoin|> #new data to use for predicitive analysis
                 select(WtpDollars,YogaFrequency,VisitLikelihood, YogaExperience,PracticeYogaInterest, MemberInterest, AgeGroup, Gender, Country) |> 
                 na.omit()

 dt <- rpart( #decison tree 
  WtpDollars ~ .,
  data = model_data2,
  method = "class")
  
  rpart.plot(
  dt,
  type = 2,
  extra = 104,
  fallen.leaves = TRUE,
  box.palette = "Greens"
)
summary(dt)
```

The decision tree shows a that at the root predicted WillingnesstoPay to be 2.99 with 100% of of respondents. The numbers underneath mean that \$0 represents 23%, \$2.99 represents 30%, \$3.99 represents 10%, \$4.99 represents 20%, and \$5.99 represents17% of all respondents. The first split shows that Yoga Frequency being less than 5 was the most important predictor. The first thing that separates willingness to pay is how frequently someone practices yoga.

The left branch shows that if there are less frequent yoga practitioners than 5 the tree predicts them answering \$2.99, but if MemberInterest is less than 3 the predicted willingness to pay is \$0. People who practice yoga less frequently and have low membership interest predict to pay \$0. These respondents are unlikely to purchase a membership. If MemberInterest is greater than 3 then the prediction changes to \$4.99 at 30%. Even if someone doesn't practice yoga very frequently high membership interest increases predicted willingness to pay.

The right branch shows YogaFrequency\>=5 these respondents are predicted to pay \$3.99 representing 27% of respondents. Frequent yoga practitioners are predicted to pay around \$3.99 regardless of membership interest in this tree.

The Decision Tree suggest that Yoga Frequency is the most important predictor and frequent practitioners are willing to pay more for a membership. Engagement level is the strongest determinant of willingness to pay. Membership interest further separated those unwilling to pay from those willing ot pay, less frequent practitioners, membership interest separates those who would pay nothing form those wiling to pay \~\$4.99.

## Cluster Analysis 1

```{r}
library(factoextra)
set.seed(123)

model_data3 <- CleanSurveyDataJoin|> #new data to use for predicitive analysis
                 select(WtpDollars,YogaFrequency, VisitLikelihood, YogaExperience,PracticeYogaInterest, MemberInterest) |> 
                 na.omit() #omit NA values

cluster_scaled <- scale(model_data3)

fviz_nbclust(
  cluster_scaled,
  kmeans,
  method = "wss"
)

##Cluster at 3 
k3 <- kmeans(
  cluster_scaled,
  centers = 3,
  nstart = 25
)


model_data3$Cluster <- factor(k3$cluster)

fviz_cluster(
  k3,
  data = cluster_scaled,
  ellipse.type = "convex"
)
```

### Elbow Plot

Noticeable bend around K=3, or K=4

### Cluster Plot

Cluseter shows respondents naturally seperate into 3 groups.

1.  Cluster (Red): Right side

2.  Cluster (Green): Small group between 2 clusters

3.  Cluster (Blue): Left side

```{r}
model_data3 %>%
  mutate(Cluster = factor(k3$cluster)) %>%
  group_by(Cluster) %>%
  summarise(across(everything(), mean))
```

### Cluster 1: Low Membership Potential

#### Characteristics:

1.  Lowest willingness to pay\~\$2.31

2.  Lowest membership interest \~1.44

3.  Lowest likelihood of visiting the website \~2.63

4.  Highest yoga experience among the clusters \~2.76

#### Marketing Strategy:

These respondents appear experience yoga practitioners but are not very interested in a Sino Yoga membership. Focus on increase value of membership, explaining membership benefits, free educational content before promoting subsriptions

### Cluster2: High Yoga Frequency but Price Sensitive

#### Characteristics:

1.  Practice yoga more frequently \~4.5

2.  Moderate willingness to pay \~2.99

3.  Moderate membership interest \~2

4.  Lower yoga experience \~2.06

#### Marketing Strategy:

These respondents appear active but not convinced of the membership value. Focus on trial memberships, beginner friendly member content, and YouTube live reminders.

### Cluster3: High Value Audience

#### Characteristics:

1.  Highest willingness to pay\~\$5.29

2.  Highest membership interest\~2.76

3.  Highest website visit likelihood \~2.63

4.  Regular yoga practitioners \~3.76

#### Marketing Strategy:

These respondents appear to be the ideal market customers. Focus on membership promotions, premium content, exclusive classes, community benefits, direct call to actions from YouTube to website.

```{r}
table(k3$cluster)

```

## Cluster Analysis 2

Performing cluster analysis again as K=2 cluster because it makes it more reliable and easier to interpret.

```{r}
library(factoextra)
set.seed(123)

model_data3 <- CleanSurveyDataJoin|> #new data to use for predicitive analysis
                 select(WtpDollars,YogaFrequency, VisitLikelihood, YogaExperience,PracticeYogaInterest, MemberInterest) |> 
                 na.omit() #omit NA values

cluster_scaled <- scale(model_data3)

fviz_nbclust(
  cluster_scaled,
  kmeans,
  method = "wss"
)

##Cluster at 2 
k2 <- kmeans(
  cluster_scaled,
  centers = 2,
  nstart = 25
)


model_data3$Cluster <- factor(k2$cluster)

fviz_cluster(
  k2,
  data = cluster_scaled,
  ellipse.type = "convex"
)
```

```{r}
model_data3 %>%
  mutate(Cluster = factor(k2$cluster)) %>%
  group_by(Cluster) %>%
  summarise(across(everything(), mean))
```

```{r}
table(k2$cluster)
```

### Cluster 1: Price Conscious Audience

#### Characteristics:

1.  Lowest willingness to pay\~\$2.35

2.  Lowest membership interest \~1.41

3.  Lowest likelihood of visiting the website \~2.65

4.  Highest yoga experience among the clusters \~2.67

#### Marketing Strategy:

These respondents appears to be interested in yoga but not convinced of the value of a membership. Focus on providing relevant free YouTube content, emphasize value of membership through testimonials, exclusive content. Use email and YouTube shorts to increase engagement before asking for membership purchases.

### Cluster2: High Value Membership Prospects

#### Characteristics:

1.  Highest willingness to pay\~\$5.16

2.  Highest membership interest\~2.78

3.  Highest website visit likelihood \~3.83

4.  Regular yoga practitioners \~2.11

#### Marketing Strategy:

These respondents appears to be Sino Yoga's highest converting audience. Focus on promoting memberships, highlighting premium member benefits, direct viewers to website with strong call to actions, offer exclusive live classes and community access.

## Cluster Analysis Importance

The strongest distinction between the clusters in engagement with the brand, not yoga behavior alone. Respondents who are more interested in Sino Yoga memberships are more likely to visit the website and also willing to pay more. Increasing user engagement with Sino Yoga is likely to have a greater impact on membership conversion than targeting demographic characteristics.
